---
title: Stock Email Report
output: 
  html_document:
    code_folding: hide
---
  
# Report for TSLA on `r Sys.Date()`

## Summary{.tabset}

```{r, echo=TRUE, message=FALSE}
library(blastula)
library(DT)
library(formattable)
library(ggplot2)
library(ggthemes)
library(highcharter)
library(quantmod)

prices <- round(getSymbols("TSLA", auto.assign = FALSE, src = "yahoo"), 2)
close <- Cl(last(prices))
open <- Op(last(prices))

recent <- last(prices, n = 90)
recent_nv <- recent[, -5]
```

The stock closed `r ifelse(close>open,'up','down')` at `r close` dollars per share yesterday.


### Price History

The chart below is made with the `quantmod` and `highcharter` R packages. An API returns all of the price history based on the stock tick symbol "TSLA." The candlestick chart is a default function from highcharter, as is the Economist theme.


```{r build_plot, echo=TRUE, warning=FALSE, message=FALSE}
highchart(type = "stock") %>%
  hc_yAxis_multiples(
    list(title = list(text = NULL), height = "75%", top = "0%"),
    list(title = list(text = NULL), height = "15%", top = "80.5%", opposite = TRUE)
  ) %>%
  hc_add_series(prices, type = "candlestick", yAxis = 0, name = "TSLA") %>%
  hc_add_series(prices[, paste0("TSLA.Volume")], name = "Volume", type = "column", yAxis = 1) %>%
  hc_add_theme(hc_theme_economist())
```

### Raw Data

The table below displays the daily price data for the stock. A concise, interactive table is created with the `DT` package. 

  
```{r show_data, echo=TRUE}
df <- as.data.frame(recent)
df[, paste0("TSLA", ".Volume")] <- df[, paste0("TSLA.Volume")] / 1000000
datatable(df) %>%
  formatCurrency(c(paste0("TSLA.Open"), paste0("TSLA", ".High"), paste0("TSLA", ".Low"), paste0("TSLA", ".Close")), digits = 2) %>%
  formatRound(c(paste0("TSLA", ".Volume")), digits = 0)
```

## Legacy Information

This report also creates a CSV file with the relevant information updated by R. The file feeds a legacy report that will slowly be replaced.

```{r write_csv, echo=TRUE}
fname <- sprintf("%s.csv", Sys.Date())
write.csv(df, file = fname)
rmarkdown::output_metadata$set(rsc_output_files = list(fname))
```

[Link to CSV](`r fname`)

## Email

This report also produces an email that is sent to key stakeholders with summary
information if the price change is above 50 cents. 

```{r send_email, warning = FALSE, message = FALSE, echo = TRUE}
# Calculate the total change
close <- Cl(last(prices, n = 2))
diff <- round(as.numeric(close[2]) - as.numeric(close[1]), 2)
subject <- sprintf("TSLA is %s today by $%g!", 
        ifelse(diff > 0,"up", "down"), 
        abs(diff))

# If the change is above a certain threshold, send an email to stake holders
# with key results embedded directly in the email
if (abs(diff) > 0.5) {
  render_connect_email(input = "stock-report-email.Rmd") %>%
  attach_connect_email(
    subject = subject,
    attach_output = TRUE,
    attachments = c(fname)
)
} else {
  blastula::suppress_scheduled_email()
}
```
